An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2022-06-30 poly-embed-journal/jmlr_cover_letter/jmlr_coverletter.tex
brainstorming reviewers

Reviewers:
\begin{itemize}
    \item Bob Williamson, University of T\"ubingen (\url{bob.williamson@uni-tuebingen.de})
    \item Shivani Agarwal, University of Pennsylviania (\url{ashivani@seas.upenn.edu})
    \item Alex Nowak-Vila, Owkin (\url{alex.nowak-vila@inria.fr})
    \item First Lastname, Institution (first.lastname@institution.edu)
    \item First Lastname, Institution (first.lastname@institution.edu)
\end{itemize}

>>>>

Reviewers:
\begin{itemize}
    \item Bob Williamson, University of T\"ubingen (\url{bob.williamson@uni-tuebingen.de})
    \item Shivani Agarwal, University of Pennsylviania (\url{ashivani@seas.upenn.edu})
    \item Alex Nowak-Vila, Owkin (\url{alex.nowak-vila@inria.fr})
    \item Tim Roughgarden, Columbia (??)(first.lastname@institution.edu)
    \item Han Bao, University of Tokyo / RIKEN AIP (first.lastname@institution.edu)
    \item Clay Scott or Yutong Wang
    \item Authors of this paper: \url{https://arxiv.org/pdf/2202.02193.pdf} -- bit of a stretch
    \item Satyen Kale
    \item Pranjal Ashwathi (see recently published ICML paper)
\end{itemize}
